---
title: "SpikeOfTheWeek"
author: "Bianca Ebanks"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A package extending the capability of [gtrendsR](https://github.com/PMassicotte/gtrendsR) 
by searching a keyword and location and showing the highest hits from the last week.

## Install

Install from GitHub with the following code:

```{r install, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("bebanks4/SpikeOfTheWeek")
```



## Usage

There is one function with two arguments for this package. 

To begin, the user must first enter the following code, inserting their keys 
where appropriate:


```

The first argument is a keyword. This will search the users desired
keyword through gtrends.

The second argument is a geo. This will seach the users desired location
through gtrends.


```{r usage, eval = FALSE}
## load SpikeOfTheWeek
library(spike_this_week)

## Run function
spike_this_week()

## This will run the package with provided defaults and produce an object in the users environment named "spike_this_week"
spike_this_week("new york knicks", "US")

## Run function with custom arguments
spike_this_week("Celtics", "CA")

## This will search "Celtics" through gtrends and show the highest hits for the last week in the choosen location, Canada "CA".
```

This function will create an object in the users enviorment called spike_this_week. This object will contain the data frame for the users chosen keyword and location or provide the data frame for the defaults. The data frame will have the hits in order of highest to lowest.
